Create data sets for modeling

### 2016-07-13 portfolio/analysis/3-createData_linear_modeling.Rmd
Filter based on strategy column

# Delete these minimal earnings
cfecnew = cfecnew[-which(paste(cfecnew$p_holder, cfecnew$year, cfecnew$p_fshy) %in% paste(permit_rev$p_holder, permit_rev$year, permit_rev$p_fshy)), ]

>>>>

# Delete these minimal earnings
nrow(cfecnew)
cfecnew = cfecnew[-which(paste(cfecnew$p_holder, cfecnew$year, cfecnew$p_spec) %in% 
  paste(permit_rev$p_holder, permit_rev$year, permit_rev$p_spec)), ]
nrow(cfecnew)
